---
title: "R Notebook"
output: html_notebook
---

Load in rerquired libraries
```{r}
library(Rmisc)
library(readxl)
library(tidyverse)
library(here)
library(tidyr)
library(janitor)

#for plotting
library(ggplot2)
library(RColorBrewer)
library(jcolors)
library(ggthemes)
library(cowplot)

#for phylo stuff
library(ape)
library(phytools)
## Use the line below if you have trouble installing ggtree with install.packages
# BiocManager::install("ggtree")
library(ggtree)

```

Read in data files
```{r}
amphData <- read_excel("TableS1_PhylogenyData.xlsx", sheet = "S1.B List of Amphibious Fishes")
amphData$Species <- sub(" ", "_", amphData$Species)

# This is the subset of the data used to make the tree showing only one node per genus
genusPlot <- read_excel("TableS1_PhylogenyData.xlsx", sheet = "S1.C GenusSelector")
genusPlot$Species <- sub(" ", "_", genusPlot$Species)
genusPlot <- genusPlot[c(1:12)]
genusPlot <- na.omit(genusPlot)

kinesub <- amphData[c(1:3,17,8,4:7,9:11)]
kinesub <- na.omit(kinesub)

```

Read in tree file
Please note that this tree was downloaded from (https://fishtreeoflife.org/downloads/)
For more information about the tree, please see (https://fishtreeoflife.org/about/) and the associated paper (https://www.nature.com/articles/s41586-018-0273-1)
```{r}
rawTree<- read.tree(file ="actinopt_12k_treePL.tre")
tree <- read.tree(file ="actinopt_12k_treePL.tre")
```

Prune data to include only fishes in the tree
```{r}
pruneData <- amphData[amphData$Species %in% tree$tip.label,]
pruneSubData <- kinesub[kinesub$Species %in% tree$tip.label,]
pruneDataGenus <- genusPlot[genusPlot$Species %in% tree$tip.label,]

SubTree <-drop.tip(tree,tree$tip.label[-match(pruneSubData$Species,
                                           tree$tip.label)])
GenusTree <-drop.tip(tree,tree$tip.label[-match(pruneDataGenus$Species,
                                           tree$tip.label)])
tree <-drop.tip(tree,tree$tip.label[-match(pruneData$Species,
                                           tree$tip.label)])
```

## This code creates plots used in the paper

Make fan trees with only one species of each genus
These trees are the raw images used for Figure 3. They were later merged in Adobe Illustrator
```{r}
tips <- as.data.frame(GenusTree$tip.label)
names(tips)[1] = "Species"
SubTest <- merge(tips, pruneDataGenus, by = "Species", sort = FALSE)

shapecols<-c("purple4","slateblue1","cadetblue1","deepskyblue","blue")
names(shapecols) <- c("tadpole","fusiform", "long", "elongate","eel-like" )
SubTest$shapecolors = shapecols[as.character(SubTest$Body.Shape)]

pdf("ShapeGenus.pdf", 8, 8)
plotTree(GenusTree,ftype="i", fsize=0.75, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$shapecolors, adj = 1, cex = 1)
dev.off()

actcols <- c("green3", "palegreen1", "grey70")
names(actcols) <- c("active", "both", "remains")
SubTest$actcolors = actcols[as.character(SubTest$Active.Passive)]

pdf("ActivityGenus.pdf", 8, 8)
plotTree(GenusTree,ftype="i", fsize=0.75, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$actcolors, adj = 1, cex = 1)
dev.off()

skincols<-c("chocolate4", "tan3", "tan")
names(skincols) <- c("armor", "scales", "skin")
SubTest$skincols = skincols[as.character(SubTest$Skin.Anatomy)]

pdf("SkinGenus.pdf", 8, 8)
plotTree(GenusTree,ftype="i", fsize=0.75, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$skincols, adj = 1, cex = 1)
dev.off()

# Body = yellow, fins = red
anatcols<-c("gold", "darkgoldenrod1","darkorange","orangered","grey70")
names(anatcols) <- c("body","body, tail","fins, body, tail", "fins, tail","not move")
SubTest$anatcols = anatcols[as.character(SubTest$Morphology.2.move)]

anatcols2<-c("firebrick1", "gold","darkorange","grey70")
names(anatcols2) <- c("apendicular", "axial",  "both", "not move" )
SubTest$anatcols2 = anatcols2[as.character(SubTest$MorphSummary)]

pdf("AnatomyGenus.pdf", 8, 8)
plotTree(GenusTree,ftype="i", fsize=0.75, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$anatcols2, adj = 1, cex = 1)
dev.off()

behavcols<-c("plum1","hotpink","grey70","red4","red3", "maroon2")
names(behavcols) <- c("crutching","jump","not move","slithering","tail pushing","walking")
SubTest$behavcols = behavcols[as.character(SubTest$Behavior)]

pdf("BehaviorGenus.pdf", 8, 8)
plotTree(GenusTree,ftype="i", fsize=0.75, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$behavcols, adj = 1, cex = 1)
dev.off()
```

This code creates the polar stacked histograms used in Figure 3
This chunk makes a historgam of Active Anatomy
```{r}
df <- read_excel("counts_rev2.xlsx", sheet = "MorphSummary")
df <- df[c(1,3,8:11)]

library(reshape2)
dft <- data.frame(segment = c("A", "B", "C",
     "D"), segpct = c(40, 30, 20, 10), Alpha = c(60,
     40, 30, 25), Beta = c(25, 30, 30, 25),
     Gamma = c(10, 20, 20, 25), Delta = c(5,
         10, 20, 25))
df$xmax <- cumsum(df$perc)
df$xmin <- df$xmax - df$perc
df$perc <- NULL
dfm <- melt(df, id = c("Body.Shape", "xmin", "xmax"))

dfm1 <- ddply(dfm, .(Body.Shape), transform, ymax = cumsum(value))
dfm1 <- ddply(dfm1, .(Body.Shape), transform,
     ymin = ymax - value)

dfm1$xtext <- with(dfm1, xmin + (xmax - xmin)/2)
dfm1$ytext <- with(dfm1, ymin + (ymax - ymin)/2)

anatcols<-c("orangered","gold", "darkorange","grey70")
names(anatcols) <- c("apendicular", "axial","both","not.move")

p1<-ggplot(dfm1, aes(ymin = ymin, ymax = ymax, xmin = xmin, xmax = xmax, 
                      fill = variable))+
  geom_rect(colour = I("white"))+
  scale_fill_manual(values=anatcols)+
  theme_classic()+
  coord_polar("x")+
  geom_text(aes(x = xtext, y = 105,
     label = paste(Body.Shape)), size = 4, angle = 45)
ggsave("ActiveAnat_rev2.pdf",p1, width = 15, height = 10, units = "cm")
```

This code creates the polar stacked histograms used in Figure 3
This chunk makes a historgram of Activity Level
```{r}
df <- read_excel("counts_rev2.xlsx", sheet = "ActivityLevel")
df <- df[c(1,3,7:9)]

library(reshape2)
dft <- data.frame(segment = c("A", "B", "C",
     "D"), segpct = c(40, 30, 20, 10), Alpha = c(60,
     40, 30, 25), Beta = c(25, 30, 30, 25),
     Gamma = c(10, 20, 20, 25), Delta = c(5,
         10, 20, 25))
df$xmax <- cumsum(df$perc)
df$xmin <- df$xmax - df$perc
df$perc <- NULL
dfm <- melt(df, id = c("Body.Shape", "xmin", "xmax"))

dfm1 <- ddply(dfm, .(Body.Shape), transform, ymax = cumsum(value))
dfm1 <- ddply(dfm1, .(Body.Shape), transform,
     ymin = ymax - value)

dfm1$xtext <- with(dfm1, xmin + (xmax - xmin)/2)
dfm1$ytext <- with(dfm1, ymin + (ymax - ymin)/2)

actcols <- c("green3", "palegreen1", "grey70")
names(actcols) <- c("active", "both", "remains")

p2<- ggplot(dfm1, aes(ymin = ymin, ymax = ymax, xmin = xmin, xmax = xmax, 
                      fill = variable))+
  geom_rect(colour = I("white"))+
  scale_fill_manual(values=actcols)+
  theme_classic()+
  coord_polar("x")+
  geom_text(aes(x = xtext, y = 105,
     label = paste(Body.Shape)), size = 4, angle = 45)
ggsave("ActivityLev_rev2.pdf",p2, width = 15, height = 10, units = "cm")
```

This code creates the polar stacked histograms used in Figure 3
This chunk makes a historgram of Behaviour
```{r}
df <- read_excel("counts_rev2.xlsx", sheet = "Behavior")
df <- df[c(1,3,10:15)]

library(reshape2)
dft <- data.frame(segment = c("A", "B", "C",
     "D"), segpct = c(40, 30, 20, 10), Alpha = c(60,
     40, 30, 25), Beta = c(25, 30, 30, 25),
     Gamma = c(10, 20, 20, 25), Delta = c(5,
         10, 20, 25))
df$xmax <- cumsum(df$perc)
df$xmin <- df$xmax - df$perc
df$perc <- NULL
dfm <- melt(df, id = c("Body.Shape", "xmin", "xmax"))

dfm1 <- ddply(dfm, .(Body.Shape), transform, ymax = cumsum(value))
dfm1 <- ddply(dfm1, .(Body.Shape), transform,
     ymin = ymax - value)

dfm1$xtext <- with(dfm1, xmin + (xmax - xmin)/2)
dfm1$ytext <- with(dfm1, ymin + (ymax - ymin)/2)

# behavcols<-c("violet","deeppink","grey70","red4","red2", "magenta2")
behavcols<-c("thistle1","maroon1","grey70","firebrick4","red", "violet")
names(behavcols) <- c("crutching","jump","not.move","slithering","tail.pushing","walking")

p3<-ggplot(dfm1, aes(ymin = ymin, ymax = ymax, xmin = xmin, xmax = xmax, 
                      fill = variable))+
  geom_rect(colour = I("white"))+
  scale_fill_manual(values=behavcols)+
  theme_classic()+
  coord_polar("x")+
  geom_text(aes(x = xtext, y = 105,
     label = paste(Body.Shape)), size = 4, angle = 45)
ggsave("Behavior_rev2.pdf",p3, width = 15, height = 10, units = "cm")
```

This is the code used to make Figure 4 showing fish lengts across taxa
```{r}

kineTest <- read_excel("TableS1.xlsx", sheet = "LengthSheet")
kineTest$Species <- sub(" ", "_", kineTest$Species)
kineTest <- na.omit(kineTest)

behavcols<-c("violet","deeppink","grey70","red4","red2", "magenta2","swim")
names(behavcols) <- c("crutching","jump","not move","slithering",
                      "tail pushing","walking","white")

behaves <- c("jump","tail pushing","slithering")

ggplot(kineTest, aes(y = log(length), x = Behavior, fill = Behavior))+
  geom_boxplot()+
  theme_classic()+
  scale_x_discrete(limits = behaves)+
  scale_fill_manual(values=behavcols)

p2<- ggplot(kineTest, aes(y = (length), x = Behavior, fill = Behavior))+
  geom_boxplot()+
  theme_classic()+
  scale_x_discrete(limits = behaves)+
  scale_fill_manual(values=behavcols)+
  theme(legend.position = "none", text = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x=element_blank(), axis.title.y=element_blank())

ggplot(kineTest, aes(y = (length), x = reorder(Behavior, length, FUN = median), fill = Behavior))+
  geom_boxplot()+
  theme_classic()+
  xlab("Behavior") + ylab("Length (cm)")+
  scale_fill_manual(values=behavcols)+
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 45, hjust = 1))+
  annotation_custom(ggplotGrob(p2), xmin = 1, xmax = 5, 
                       ymin =250, ymax = 1000)
ggsave("LengthAll_Inset.pdf", width = 20, height = 15, units = "cm")

kineTest<- kineTest %>% 
  mutate(V5 = case_when(Body.Shape == "fusiform" ~ (4/3)*pi*(0.0125*length), 
                        Body.Shape == "tadpole" ~ (pi*((0.2*length)^2)*length)/3,
                        Body.Shape == "long" ~ pi*length*(0.1*length),
                        Body.Shape == "elongate" ~ pi*length*(0.05*length),
                        Body.Shape == "eel-like" ~ pi*length*(0.01*length),
                        TRUE ~ 0))

```

This code is used to count instances of categoral variables. It was used to make the count table (S1.D Group Counts)
```{r}
test = kinesub %>% count(Body.Shape)
test$np = (test$n/nrow(kinesub))*100

test2<-kinesub %>%                           # case linelist
  tabyl(Body.Shape, MorphSummary) %>%        # cross-tabulate counts of two columns
  adorn_totals(where = "row") %>%            # add a total row
  # adorn_percentages(denominator = "col") %>% # convert to proportions w/col denominator
  # adorn_pct_formatting() %>%                 # convert proportions to percents
  # adorn_ns(position = "front") %>%           # display as: "count (percent)"
  adorn_title(                               # adjust titles
    row_name = "Body.Shape",
    col_name = "Emersion.Tolerance")
```

## This is extra code which generates plots not used in the paper. 
We included it here, as it might be of interest/use

Substet data for dot tree of all Amph Data
```{r}
cols<-setNames(c("deepskyblue1","blue ","purple4 ","dodgerblue1 ","blueviolet ","skyblue2",
                 "greenyellow","green","springgreen3","green4","yellow",
                 "grey60","grey100","grey20"),
                c("fusiform","long","eel-like","tadpole","elongate","deep",
                 "fresh", "euryhaline","marine","brackish","all",
                 "both", "remains", "active"))

x = as.matrix(pruneData$Body.Shape)
y = as.matrix(pruneData$Water.Type)
z = as.matrix(pruneData$Active.Passive)

Y = cbind(x,y,z)
```

Plot dot tree of all Amph Data
```{r}
pdf("Amph_test.pdf", 20, 20)
rownames(Y) <- (pruneData$Species)
dotTree(tree,Y, colors=cols, x.space = 0.05, leg.space = 0.001)

dev.off()
```

Subset data for Genus tree
```{r}
cols2<-setNames(c("deepskyblue1","blue ","purple4 ","dodgerblue1 ","blueviolet ","skyblue2",
                 "tan4","tan2","tan",
                 "palegreen1", "grey70", "green3",
                 "darkseagreen1", "springgreen", "springgreen4", "turquoise", "gray70",
                 "violet", "deeppink","gray70","darkviolet","darkorchid","deeppink3"),
                c("fusiform","long","eel-like","tadpole","elongate","deep",
                 "armor",  "scales", "skin" ,
                 "both", "remains", "active",
                 "body","body, tail", "fins, tail, body", "fins, tail", "not move",
                 "crutching", "jump", "not move", "slithering", "tail pushing", "walking" ))

a = as.matrix(pruneDataGenus$Body.Shape)
b = as.matrix(pruneDataGenus$Skin.Anatomy)
c = as.matrix(pruneDataGenus$Active.Passive)
d = as.matrix(pruneDataGenus$Morphology.2.move)
e = as.matrix(pruneDataGenus$Behavior)

Y3 = cbind(a,b,c,d,e)
```

Plot the Genus Tree
```{r}
pdf("GenusTest.pdf", 20, 20)
rownames(Y3) <- (pruneDataGenus$Species)
dotTree(GenusTree,Y3, colors=cols2, x.space = 0.05, leg.space = 0.001)

dev.off()
```

Make fan trees of entire dataset
These are not used in the paper, as they include multiple species in the same genus, but they might be of interest
```{r}
ggtree(tree, layout='circular') + geom_tiplab(as_ylab=TRUE, size = 0.1)

X <- as.data.frame(pruneData$Body.Shape)
rownames(X) <- pruneData$Species

tips <- as.data.frame(tree$tip.label)
names(tips)[1] = "Species"
test <- merge(tips, pruneData, by = "Species", sort = FALSE)

shapecols<-c("green4","seagreen1 ","cadetblue1 ","deepskyblue ","mediumblue")
names(shapecols) <- c("tadpole","fusiform", "long", "elongate","eel-like" )
test$shapecolors = shapecols[as.character(test$Body.Shape)]

actcols <- c("green3", "palegreen1", "grey50")
names(actcols) <- c("active", "both", "remains")
test$actcolors = actcols[as.character(test$Active.Passive)]

pdf("ShapeCirc.pdf", 8, 8)
plotTree(tree,ftype="i", fsize=0.5, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=test$shapecolors, adj = 1, cex = 1)
dev.off()

pdf("ActCirc.pdf", 8, 8)
plotTree(tree,ftype="i", fsize=0.5, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=test$actcolors, adj = 1, cex = 1)
dev.off()
```

Make fan trees of entire dataset
These are not used in the paper, as they include multiple species in the same genus, but they might be of interest
```{r}
tips <- as.data.frame(SubTree$tip.label)
names(tips)[1] = "Species"
SubTest <- merge(tips, pruneSubData, by = "Species", sort = FALSE)


shapecols<-c("purple4","slateblue1","cadetblue1","deepskyblue","blue")
names(shapecols) <- c("tadpole","fusiform", "long", "elongate","eel-like" )
SubTest$shapecolors = shapecols[as.character(SubTest$Body.Shape)]

pdf("SubShapeCirc.pdf", 8, 8)
plotTree(SubTree,ftype="i", fsize=0.5, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$shapecolors, adj = 1, cex = 1)
dev.off()

actcols <- c("green3", "palegreen1", "grey70")
names(actcols) <- c("active", "both", "remains")
SubTest$actcolors = actcols[as.character(SubTest$Active.Passive)]

pdf("SubActCirc.pdf", 8, 8)
plotTree(SubTree,ftype="i", fsize=0.5, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$actcolors, adj = 1, cex = 1)
dev.off()

skincols<-c("chocolate4", "tan3", "tan")
names(skincols) <- c("armor", "scales", "skin")
SubTest$skincols = skincols[as.character(SubTest$Skin.Anatomy)]

pdf("SubSkinCirc.pdf", 8, 8)
plotTree(SubTree,ftype="i", fsize=0.5, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$skincols, adj = 1, cex = 1)
dev.off()

# Body = yellow, fins = red
anatcols<-c("gold", "darkgoldenrod1","darkorange","orangered","grey70")
names(anatcols) <- c("body","body, tail","fins, body, tail", "fins, tail","not move")
SubTest$anatcols = anatcols[as.character(SubTest$Morphology.2.move)]

anatcols2<-c("firebrick1", "gold","darkorange","grey70")
names(anatcols2) <- c("apendicular", "axial",  "both", "not move" )
SubTest$anatcols2 = anatcols2[as.character(SubTest$MorphSummary)]

pdf("SubAnatCirc2.pdf", 8, 8)
plotTree(SubTree,ftype="i", fsize=0.5, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$anatcols2, adj = 1, cex = 1)
dev.off()

# Body = red, fins = pink
behavcols<-c("violet","deeppink","grey70","red4","red2", "magenta2")
names(behavcols) <- c("crutching","jump","not move","slithering","tail pushing","walking")
SubTest$behavcols = behavcols[as.character(SubTest$Behavior)]

pdf("SubBehavCirc.pdf", 8, 8)
plotTree(SubTree,ftype="i", fsize=0.5, lwd=2,type="fan",label.offset = 50)
tiplabels(pch = 19, col=SubTest$behavcols, adj = 1, cex = 1)
dev.off()
```

These stacked histograms show counts of all categorical data. 
they are not used in the paper, but might be of interest.
```{r}
behavcols<-c("violet","deeppink","grey70","red4","red2", "magenta2")
names(behavcols) <- c("crutching","jump","not move","slithering","tail pushing","walking")

anatcols<-c("gold","orangered", "darkorange","grey70")
names(anatcols) <- c("apendicular", "axial","both","not move")

actcols <- c("green3", "palegreen1", "grey70")
names(actcols) <- c("active", "both", "remains")

shapes <- c("tadpole", "fusiform", "long", "elongate","eel-like")
p1<- ggplot(kinesub, aes(x = Body.Shape, fill = MorphSummary))+
  geom_bar(position="fill")+theme_classic()+
  scale_fill_manual(values=anatcols2)+ 
  scale_x_discrete(limits = shapes)+
  theme(axis.text.x = element_text(size = 14),
      text = element_text(size=20))+
  xlab("Body Shape") + ylab("Percent") + labs(fill = "Active Anatomy")

p2<- ggplot(kinesub, aes(x = Body.Shape, fill = Behavior))+
  geom_bar(position="fill")+theme_classic()+
  scale_fill_manual(values=behavcols)+ 
  scale_x_discrete(limits = shapes)+
  theme(axis.text.x = element_text(size = 14),
      text = element_text(size=20))+
  xlab("Body Shape") + ylab("Percent") + labs(fill = "Behavior")

p3 <- ggplot(kinesub, aes(x = Body.Shape, fill = Active.Passive))+
  geom_bar(position="fill")+theme_classic()+
  scale_fill_manual(values=actcols)+ 
  scale_x_discrete(limits = shapes)+
  theme(axis.text.x = element_text(size = 14),
      text = element_text(size=20))+
  xlab("Body Shape") + ylab("Percent") + labs(fill = "Activity")

p4<- ggplot(kinesub, aes(x = Active.Passive, fill = MorphSummary))+
  geom_bar(position="fill")+theme_classic()+
  scale_fill_manual(values=anatcols2)+ 
  theme(axis.text.x = element_text(size = 14),
      text = element_text(size=20))+
  xlab("Activity") + ylab("Percent") + labs(fill = "Active Anatomy")

p5<- ggplot(kinesub, aes(x = Active.Passive, fill = Behavior))+
  geom_bar(position="fill")+theme_classic()+
  scale_fill_manual(values=behavcols)+ 
  theme(axis.text.x = element_text(size = 14),
      text = element_text(size=20))+
  xlab("Activity") + ylab("Percent") + labs(fill = "Behavior")

p6<- ggplot(kinesub, aes(x = MorphSummary, fill = Behavior))+
  geom_bar(position="fill")+theme_classic()+
  scale_fill_manual(values=behavcols)+ 
  theme(axis.text.x = element_text(size = 14),
      text = element_text(size=20))+
  xlab("Active Anatomy") + ylab("Percent") + labs(fill = "Activity")

plot_grid(
  p3,p6,
  p1,p4,
  p2,p5,
  labels = "AUTO", ncol = 2
)
ggsave("compAll.pdf", width = 40, height = 20, units = "cm")

```

This code creates a stacked histogram showing Emersion time. It was not used in the paper, but might be of interest.
```{r}
df <- read_excel("counts_rev2.xlsx", sheet = "Emersion")
df <- df[c(1,3,10:15)]

library(reshape2)
dft <- data.frame(segment = c("A", "B", "C",
     "D"), segpct = c(40, 30, 20, 10), Alpha = c(60,
     40, 30, 25), Beta = c(25, 30, 30, 25),
     Gamma = c(10, 20, 20, 25), Delta = c(5,
         10, 20, 25))
df$xmax <- cumsum(df$perc)
df$xmin <- df$xmax - df$perc
df$perc <- NULL
dfm <- melt(df, id = c("Body.Shape", "xmin", "xmax"))

dfm1 <- ddply(dfm, .(Body.Shape), transform, ymax = cumsum(value))
dfm1 <- ddply(dfm1, .(Body.Shape), transform,
     ymin = ymax - value)

dfm1$xtext <- with(dfm1, xmin + (xmax - xmin)/2)
dfm1$ytext <- with(dfm1, ymin + (ymax - ymin)/2)

# behavcols<-c("violet","deeppink","grey70","red4","red2", "magenta2")
# names(behavcols) <- c("crutching","jump","not.move","slithering","tail.pushing","walking")

p3<- ggplot(dfm1, aes(ymin = ymin, ymax = ymax, xmin = xmin, xmax = xmax, 
                      fill = variable))+
  geom_rect(colour = I("white"))+
  scale_fill_brewer(type = "seq")+
  theme_classic()+
  coord_polar("x")+
  geom_text(aes(x = xtext, y = 105,
     label = paste(Body.Shape)), size = 4, angle = 45)
ggsave("Emersion_rev2.png",p3, width = 15, height = 10, units = "cm")
```
